\documentclass[]{friggeri-cv}
\usepackage{xcolor}
\usepackage{multicol}

% \addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\header{Tim}{Visée}{Software Engineer}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside}
\section{Me}
\href{https://timvisee.com/}{timvisee.com}
\href{https://github.com/timvisee}{\textcolor{red}{github://}timvisee}
\href{https://gitlab.com/timvisee}{gitlab://timvisee}
\href{https://stackoverflow.com/users/1000145}{so://timvisee}
\href{https://linkedin.com/in/timvisee}{linkedin://timvisee}
\href{https://twitter.com/timvisee}{twitter://timvisee}
\href{https://keybase.io/timvisee}{keybase://timvisee}
\section{Contact}
\href{mailto:tim@visee.me}{tim@visee.me}
+31 6 4817 9579
~
Goudsbloemlaan 69
The Hague, 2565 CP
The Netherlands
\section{Languages}
Dutch, English
\section{Real languages}
% {\color{red} $\varheartsuit$} Rust
Rust, C, C++
Java, C\#
PHP, HTML, JavaScript
Bash
Python, Go
\section{Technologies}
Linux, Docker
Git, Vim
\LaTeX{}
~
\textit{\href{https://github.com/timvisee/cv}{</>}}
\end{aside}

%----------------------------------------------------------------------------------------
%	ABOUT SECTION
%----------------------------------------------------------------------------------------

\section{About}
\begin{multicols}{2}
\begin{itemize}
  \tightlist{}
  \item Open-source \& free \\software enthusiast
  \item Linux fanatic
  \item Rust evangelist
  \item Git master
  \item Vim wizard
\end{itemize}
\end{multicols}

Self-educated software engineer started at 8 years old, always looking to expand
my technical knowledge with challenging projects.\\
Drive to built reliable, secure, robust \& high-performance software with the
best technologies available to make the digital world a better place.
Always searching for innovative solutions to develop software not just for
robots, but also for humans.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry
{2009 -- 2014}
{HAVO {\normalfont (completed)}}
{Christelijk College de Populier}
{Dutch \textperiodcentered{} English \textperiodcentered{} Physics \textperiodcentered{} Mathematics B \textperiodcentered{} Chemistry \textperiodcentered{} NLT}

%------------------------------------------------

\entry
{2014 -- 2015}
{Computer Science {\normalfont (not finished)}}
{The Hague University of Applied Sciences}
%{TODO some details...}

%------------------------------------------------

\entry
{2015 -- now}
{HBO-ICT {\normalfont (current)}}
{The Hague University of Applied Sciences}
{Specialization: Software Engineering}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Work}

\begin{entrylist}

%------------------------------------------------

\entry
{2018 -- now}
{Intermax Cloudsourcing}
{Rotterdam, The Netherlands}
{\emph{Software Engineer} \\
Time: 8 to 24 hours / week}

%------------------------------------------------

\entry
{2017 (6mth)}
{Intermax Cloudsourcing}
{Rotterdam, The Netherlands}
{\emph{Internship Software Engineer} \\
Time: 40 hours / week}

%------------------------------------------------

\entry
{2015 (4mth)}
{Hyperion Technologies}
{Delft, The Netherlands}
{\emph{Software Engineer \& PCB Assembler} \\
Time: 36 hours / week}

%------------------------------------------------

\entry
{2014 (4mth)}
{SystematIC Design}
{Delft, The Netherlands}
{\emph{System Administrator} \\
Time: 24 hours / week}

%------------------------------------------------

\end{entrylist}

\subsection{Private}

\begin{entrylist}

%------------------------------------------------

\entry
{2006 -- now}
{Freelancer, Self-employed}
{The Hague, The Netherlands}
{\emph{Freelancer, Software Engineer} \\
Time: 24 hours / week}

%------------------------------------------------

\end{entrylist}

\newpage{}

%----------------------------------------------------------------------------------------
%	KNOWLEDGE SECTION
%----------------------------------------------------------------------------------------

\section{Knowledge}

Excellent experience with application development with a broad selection of
languages, including:

\begin{multicols}{3}
\begin{itemize}
  \tightlist{}
  \item Rust
  \item Java
  \item PHP
  \item C
  \item C++
  \item C\#
  \item JavaScript
\end{itemize}
\end{multicols}

Excellent knowledge of operating systems such as:

\begin{multicols}{3}
\begin{itemize}
  \tightlist{}
  \item Linux
  \item Microsoft Windows
  \item macOS
  \item Android
\end{itemize}
\end{multicols}

Excellent experience with containerization using Docker and related.

Experienced with databases systems and related such as:

\begin{multicols}{3}
\begin{itemize}
  \tightlist{}
  \item MySQL
  \item PostgreSQL
  \item MongoDB
  \item SQLite
  \item Redis
\end{itemize}
\end{multicols}

Excellent experience with Continuous Integration and Continuous Deployment.

Knowledge of Scrum and Kanban techniques.

Leader at a scouts group, de Mohicanen.

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\textbf{Professional:}
\begin{multicols}{2}
\begin{itemize}
  \tightlist{}
  \item Application development
  \item Computer programming
\end{itemize}
\end{multicols}


\textbf{Personal:}
\begin{multicols}{2}
\begin{itemize}
  \tightlist{}
  \item Graphics design, layouts/logos
  \item Scouting
  \item Technical Do It Yourself projects
\end{itemize}
\end{multicols}

\newpage{}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

These are some of the projects I work or have worked on:

\begin{entrylist}

\entry
{2018 -- now}
{\href{https://github.com/timvisee/barbapappa}{BARbapAPPa}}
{}
{Digital bar administration, transaction and payment platform.}

\entry
{2018 -- now}
{\href{https://github.com/timvisee/ffsend}{ffsend}}
{}
{Easily and securely share files from the command line. A fully featured Firefox Send client.}

\entry
{2012 -- now}
{Rumor}
{}
{Decentralised open-source Instant Messaging alternative.}

\entry
{2017 -- now}
{Pokoebox}
{}
{Smart portable boombox which includes video streaming.}

\entry
{2017}
{\href{https://github.com/timvisee/dworek}{dworek}}
{}
{Real-time location based web game. Players build factories to produce items,
trade and capture premises.}

\entry
{2017}
{\href{https://github.com/timvisee/maris-game}{Maris game}}
{}
{Real-time location based web game. Players have to complete challenges.}
% TODO: mention this is for Maris

\entry
{2016}
{\href{https://github.com/timvisee/voxeltex-engine}{VoxelTex Engine}}
{}
{A 3D engine from scratch using OpenGL.}

\entry
{2015}
{Carbon CMS}
{}
{Content Management System for PHP websites.}

\end{entrylist}

For a more complete view I recommend to check out my
\href{https://github.com/timvisee}{GitHub}
profile.

%----------------------------------------------------------------------------------------
%	DIPLOMAS SECTION
%----------------------------------------------------------------------------------------

\section{Diplomas}

\begin{entrylist}

%------------------------------------------------

\entry
{2014}
{HAVO}
{Christelijk College de Populier}
% {Awarded after completing 5 years of college.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Communication skills}

\begin{entrylist}

%------------------------------------------------

\entry
{2017}
{Communicative training}
{Intermax Cloudsourcing}
% {TODO Some description here}

%------------------------------------------------

\entry
{2015}
{Presentations}
{The Hague University of Applied Sciences}
% {TODO Some description here}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
% REFERENCE SECTION
%----------------------------------------------------------------------------------------

\section{References}

\begin{entrylist}

\entry
{\href{https://intermax.nl}{Intermax}}
{M. van Gorp}
{Schouwburgplein 30, 3012 CL Rotterdam }
{\emph{Software Engineer} \\
Mail: m.vangorp@intermax.nl, Phone: +31 10 710 4444 }

\entry
{\href{https://systematic.nl}{SystematIC}}
{R. Visée}
{Elektronicaweg 20, 2628 XG Delft}
{\emph{Director} \\
Mail: contact@systematic.nl, Phone: +31 15 2511100}

\entry
{\href{https://hyperiontechnologies.nl/}{Hyperion}}
{B. Monna}
{Motorenweg 5H, 2623 CR Delft}
{\emph{Director} \\
Mail: info@hyperiontechnologies.nl, Phone: +31 15 5160905}

\end{entrylist}

% TODO: properly define favorite programming languages and technologies
% TODO: text description of experiences/hobbies
% TODO: own projects
% TODO: company references
% TODO: resolve all other TODOs

\end{document}
